---
title: "EDA"
author: Cory Lowe
date: May  28, 2024
output:  github_document
---

# IMPORT LIBRARIES

```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
```

# IMPORT DATA

```{r}
df_customers <- read.csv("../02_data/ifood_df.csv")

df_customers <- df_customers %>%
  mutate(AcceptedCmp1 = factor(if_else(AcceptedCmp1 == 1, "True", "False"))) %>%
  mutate(AcceptedCmp2 = factor(if_else(AcceptedCmp2 == 1, "True", "False"))) %>%
  mutate(AcceptedCmp3 = factor(if_else(AcceptedCmp3 == 1, "True", "False"))) %>%
  mutate(AcceptedCmp4 = factor(if_else(AcceptedCmp4 == 1, "True", "False"))) %>%
  mutate(AcceptedCmp5 = factor(if_else(AcceptedCmp5 == 1, "True", "False"))) %>%
  mutate(Response = factor(if_else(Response == 1, "True", "False"))) %>%
  mutate(Complain = factor(if_else(Complain == 1, "True", "False"))) %>%
  mutate(education_2n.Cycle = factor(if_else(education_2n.Cycle == 1, "True", "False"))) %>%
  mutate(education_Basic = factor(if_else(education_Basic == 1, "True", "False"))) %>%
  mutate(education_Graduation = factor(if_else(education_Graduation == 1, "True", "False"))) %>%
  mutate(education_Master = factor(if_else(education_Master == 1, "True", "False"))) %>%
  mutate(education_PhD = factor(if_else(education_PhD == 1, "True", "False")))
  
```

# INITIAL LOOK AT DATA

```{r}
summary(df_customers)
```

```{r}
head(df_customers)
```

# CAMPAIGN SUCCESS VARIABLE

```{r}
df_customers %>%
  ggplot(aes(x = Response)) +
  geom_bar(aes(fill = Response))
```

-   "Response variables" much higher proportion than "AcceptedCmp" variables.

```{r}
df_customers %>%
  ggplot(aes(x = AcceptedCmp1)) +
  geom_bar(aes(fill = AcceptedCmp1))
```

```{r}
df_customers %>%
  ggplot(aes(x = AcceptedCmp2)) +
  geom_bar(aes(fill = AcceptedCmp2))
```

```{r}
df_customers %>%
  ggplot(aes(x = AcceptedCmp3)) +
  geom_bar(aes(fill = AcceptedCmp3))
```

```{r}
df_customers %>%
  ggplot(aes(x = AcceptedCmp4)) +
  geom_bar(aes(fill = AcceptedCmp4))
```

```{r}
df_customers %>%
  ggplot(aes(x = AcceptedCmp5)) +
  geom_bar(aes(fill = AcceptedCmp5))
```

# COMPLAIN

```{r}
df_customers %>%
  ggplot(aes(x = Complain)) +
  geom_bar(aes(fill = Complain))
```

# CUSTOMER DAYS

```{r}
df_customers %>%
  ggplot(aes(x = Customer_Days)) +
  geom_bar()

df_customers %>%
  ggplot(aes(x = Customer_Days)) +
  geom_histogram(bins = 70)
```

-   DtCustomer variable missing. This must be the replacement one.
-   This looks pretty consistant, meaning the campaigns were launched consistently.

# EDUCATION

```{r}
df_customers %>%
  ggplot(aes(x = education_2n.Cycle)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = education_Basic)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = education_Graduation)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = education_Master)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = education_PhD)) +
  geom_bar()
```

```{r eval=FALSE}
tmp_education_cnt <- rowSums(df_customers[, c("education_2n.Cycle", "education_Basic", "education_Graduation", "education_Master", "education_PhD")])

print("All educations are coded zero (doesn't have), or 1 (does have).")
print("I need to confirm if each person has 1 and only one education level (i.e. mutually exclusive educations and no missed codings")
print(head(tmp_education_cnt))

print("Min =1 means everyone has at least 1 education")
min(tmp_education_cnt)

print("Max = 1 means everyone has at most 1 education")
max(tmp_education_cnt)

print("Therefore, we can deduce that everyone has one educational level.")

rm(tmp_education_cnt)
```

*This block doesn't run, as the variables were turned into factors (at the data import stage), so when plotting, the true false factors would be on a discrete axis (vs a continuous 0 / 1 axis.)*

```{r eval=FALSE}
tmp_marital_cnt <- rowSums(df_customers[, c("marital_Divorced", "marital_Married", "marital_Single", "marital_Together", "marital_Widow")])

print("All marital are coded zero (doesn't have), or 1 (does have).")
print("I need to confirm if each person has 1 and only one marital level (i.e. mutually exclusive marital status and no missed codings")

min(tmp_marital_cnt)

max(tmp_marital_cnt)

rm(tmp_marital_cnt)
```
*This block doesn't run, as the variables were turned into factors (at the data import stage), so when plotting, the true false factors would be on a discrete axis (vs a continuous 0 / 1 axis.)*

```{r}
df_customers %>%
  ggplot(aes(x = marital_Divorced)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = marital_Married)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = marital_Single)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = marital_Together)) +
  geom_bar()
```

```{r}
df_customers %>%
  ggplot(aes(x = marital_Widow)) +
  geom_bar()
```
